\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-03-12 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
section 1 updated

Material properties in control volume finite element methods (Fig.\ref{fig:fem_cv}, describes the $P_{1}DGP_{2}$ element type) may vary abruptly (permeability and/or porosity contrasts at fracture-matrix interfaces). Since geometries are captured by finite elements (FE), constructed control volumes (CV) typically extend over the interfaces which may have different properties. Therefore, some average value of the permeability (defined in the FE space but projected into the CV space) is applied across the CVs at these interface. This often leads to excessive numerical dispersion especially in highly heterogeneous media. In order to overcome such artificial numerical dispersion, discontinuous hybrid finite element finite volume method (DFEFVM) was developed by \citet{nick_2011b, nick_2011a}. This novel discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials. \citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}. Fluxes over CV's were calculated based upon material properties, whereas the saturation fields were volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.

>>>>

Through the $P_{1}DGP_{2}$ element type, material properties can be described using the control volume finite element methods (Fig.\ref{fig:fem_cv}. %describes the $P_{1}DGP_{2}$ element type may vary abruptly (permeability and/or porosity contrasts at fracture-matrix interfaces). 
Since geometries are captured by finite elements, constructed control volumes typically extend over the interfaces which may have different properties. Therefore, some average value of the permeability (defined in the FE space but projected into the CV space) is applied across the CVs at these interfaces. This often leads to excessive numerical dispersion especially in highly heterogeneous media. In order to overcome such artificial numerical dispersion, discontinuous hybrid finite element finite volume method (DFEFVM) was developed by \citet{nick_2011b, nick_2011a}. This novel discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials. \citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}. Fluxes over CV's were calculated based upon material properties, whereas the saturation fields were volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.
